---
title: "Correlations between Candidate Models and previously established Models"
author: "Vinita Vader"
format:
  html:
    toc: true
    toc-location: left
    tbl-colwidths: [40, 30, 30]
    number-sections: true
    css: styles.css
editor: visual
---

```{r}
#| include: false
knitr::opts_chunk$set(message = FALSE, warning = FALSE)
```

# Addendum 1

We will generate correlations matrices showing the relation to the 1, 5, 8, and 13-factor models' variables to the following 'external/etic variables': the Dutch and the German type-noun factors, the Big Five, Big Three, Big Two, and Big One structures as well the Multi-Language Seven set.

# Import data

```{r message=FALSE,warning=FALSE}
library(tidyverse)
#data with all fs and type-nouns 
data <- rio::import(here::here("data", "typenoun.sav"), setclass = "tbl_df") %>% 
  rio::characterize() %>% 
  janitor::clean_names()

#data.frame(names(data)) %>% View

#data for the factor scores of 1,5,8,13 and 32 factor candidate models 
fs_candModels <- rio::import(here::here("data", "typenoun_FSonly1_5_8_13_32.xlsx"), setclass = "tbl_df") %>%   
  rio::characterize() %>%   
  janitor::clean_names()

#names(fs_candModels)

factor_labels_RAWtable <- rio::import(here::here("data","correct_order_factors.xlsx"), setclass = "tbl_df")%>%   
  rio::characterize() %>%   
  janitor::clean_names()

options(dplyr.print_max = 1e9)
```

# Functions

```{r}
#function for selecting variables for fs_candModels data
select_Vars <- function(varNames){
  fs_candModels %>% 
    dplyr::select_at(vars(all_of((varNames))))
}

#function for electing variables for etic models
select_Vars2 <- function(varNames){
  data %>% 
    dplyr::select_at(vars(all_of((varNames))))
}

#creating dataframes for etic vars
create_df <- function(string, no_vars){
  var_string <- c(paste0({{string}}, 1:no_vars))
  df <- select_Vars2(var_string)
  df
}

#convert cors -> 2 decimal places; used as a function for the funk below
round_df <- function(cor_df){
  cor_df %>% 
    as.data.frame() %>% 
   as_tibble() %>% 
 mutate_if(., is.numeric, round ,2)
}

#correlation across lists 
all_corr_mats <- function(etic_list){
  cross2(list_fs, etic_list) %>%   
   invoke_map(cor, .) %>%  
   map(., as_tibble, rownames = "cand_model") %>% 
   map(., round_df) #cors -> 2 decimal places
  
}

#a neat correlation table with a diagonal
neatCortab <- function(corMat){

  #corMat here is a tibble with one col as the candidate models
  data = corMat %>% 
     mutate_if(is.numeric, round, 3)
 
  #get the col names
  var_names <- data %>% 
      select_if(is.numeric) %>% 
      names()
 
 #function to rearrange the correlation matrices  
abv.4_allCols <-  function(var){
    var <- sym(var) #allows a string (e.g., "col1" to be evaluated as the a variable name)
    data %>% 
      #arrange the df acc to the specified col in desc order
     arrange(desc(abs(!!{{var}}))) %>% 
     filter(abs(!!{{var}}) >= .4)
  }
  
  #get list of all the  ≥.4 values for every col
all_.4 <- map(var_names, abv.4_allCols)
  
  #merge all the lists and retain only distinct rows
partDF_.4 <- all_.4 %>%  map_df(bind_rows) %>% distinct()
  
  #add the remaining rows from the original df
final_df <- right_join(partDF_.4, data)

final_df
}
```

# Emic variables

```{r}
var_names_string <- function(actual_string){
   extract_no <- str_extract_all({{actual_string}},"\\(?[0-9,.]+\\)?") %>% 
    unlist() %>% 
    as.numeric()
   
   var_names <- paste0({{actual_string}}, 1:extract_no)
    var_names
}


#build a list with all factor scores(fs) of candidate models 
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"))

#list of all variable names for all candidate models
fs_var_names <- map(cand_model_names, var_names_string)

#list of all factor scores for all emic - solutions in the paper - variables
list_fs <- map(fs_var_names, select_Vars)
```

# Etic variables

### German

**German male-target factors**

-   M1 - Weakling, Sissy, Chicken, Coward, Softy

-   M2 - Smart-aleck, Wise-guy, Pain-in-the-neck, Liar, Loudmouth

-   M3 - Thinker, Intellectual, Genius, Egghead, Quick-thinker

-   M4 - Joker, Clown, Comedian, Life-of-the-party, Jester

-   M5 - Ladies'-man, Lady-killer, Playboy, Stud, Womanizer

-   M6 - Recluse, Loner, Skeptic, Nag, Individual

-   M7 - Stickler, Careerist, Born-fighter, High-flier

```{r}
german_man_df <- create_df("sc_gm", 7)
```

**German female-target factors**

-   F1 - Loudmouth, Nag, Nuisance, Pest, Pain-in-the-neck

-   F2 - Thinker, Authority, Intellectual, Egghead, Quick-thinker

-   F3 - Joker, Comedian, Life-of-the-party, Pal

-   F4 - Conservative, Bore, Sleephead, Coward, Hanger-on

-   F5 - Pessimist, Chicken, Dreamer, Daydreamer, Skeptic

-   F6 - Beauty, Careerist, Materialist, Sex-object, Fashion-plate

```{r}
german_woman_df <- create_df("sc_gw", 6) 
```

```{r}
german_list<- list(german_man_df, german_woman_df)

german_cors <- all_corr_mats(german_list)

#sheet names
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), times = 2)

mw_string <- rep(c("_m","_w"), each = 5)

names(german_cors) <- str_c(cand_model_names , mw_string)


#publication ready table
neat_pub_table <- function(data){
  
  #rearranges the cor mats in a clustered/diagonal format
  neat_cors <- map(data, neatCortab)
  
  #additional cols - factor labels, type-nouns
factor_labels_table <- factor_labels_RAWtable %>% 
  mutate(model = factor(model, levels= unique(model))) %>% 
  group_split(model)


names(factor_labels_table) <- c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob")

#Join the neat table with all the labels
joined_tables <- Map(left_join, neat_cors, factor_labels_table)

select_cols <- function(df){
  df %>% 
    dplyr::select(-model) %>% 
  dplyr::select(cand_model, factor_labels, type_nouns, everything())
  
}

final_neat_cors <- map(joined_tables, select_cols)
final_neat_cors

}

neat_pub_german <- neat_pub_table(german_cors)
```

```{r, results='asis'}
map(neat_pub_german, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

```{r eval=FALSE}
#Write in excel sheet to send 
export_list <- function(list_name){
  filename <- paste0("/Users/vinitavader/Desktop/EnglishTypeNoun-Lexical-Study/data/tables/etic_vars_cor/",{{list_name}},".xlsx")
  
  rio::export(eval(parse(text = {{list_name}})), check.rows = FALSE, filename)
}

export_list("neat_pub_german") 
```

### Dutch

**Dutch self factors**

-   Malignity - Cheater, Monster, Arch-villain, False-friend

-   Anxiety - Chicken, Scaredy-cat, Coward, Bore

-   Extraversion - Boaster, Merrymaker, Chatterer, Chatterbox

-   Culture - Strategist, Philosopher, Thinker, Intellectual

-   Antagonism - Troublemaker, Nuisance, Obstructionist, Oppositionalist

-   Perseverance - Go-getter, Worker, Workhorse

-   Materialism - Capitalist, Leader, Authority, Boss

```{r}
dutch_self_df <- create_df("sc_ds", 7) 
```

**Dutch-partner factors** Malignity - Monster, Moron, Vandal, Pain-in-the-neck Extraversion - Clown, Comedian, Merrymaker Anxiety - Scaredy-cat, Worrywart, Coward, Chicken Antagonism - Know-it-all, Oppositionalist, Obstructionist Culture - Philosopher, Poet, Intellectual, Anarchist Perseverance - Go-getter, Fighter, Worker, Workhorse Colourlessness - Stoic, Pragmatist, Chameleon, Softy

```{r}
dutch_peer_df <- create_df("sc_dp", 7) 
```

```{r}
dutch_list<- list(dutch_self_df, dutch_peer_df)

dutch_cors <- all_corr_mats(dutch_list)

#sheet names
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), times = 2)

sp_string <- rep(c("_s","_p"), each = 5)

names(dutch_cors) <- str_c(cand_model_names, sp_string)


neat_pub_dutch <- neat_pub_table(dutch_cors)
```

```{r results='asis'}
map(neat_pub_dutch, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

```{r eval=FALSE}
#Write in excel sheet to send 
export_list("neat_pub_dutch") 
```

### Big 5

**Big Five factors**

-   Extraversion - Bold, Talkative, Sociable versus Bashful, Shy, Timid

-   Agreeableness - Warm, Tolerant, Lenient versus Harsh, Stern, Cruel, Sly

-   Conscientiousness - Organized, Logical, Firm versus Disorganized, Unsystematic, Scatterbrained

-   Emotional Stability - Anxious, Fearful, Emotional, Jealous

-   Intellect - Philosophical, Complex, Clever, Unconventional versus Conventional, Traditional, Unreflective

```{r}
#make a df of the Big 5 only 
big5_var<- c("scb5_i","scb5_ii","scb5_iii","scb5_iv","scb5_v")
big5_df <- select_Vars2(big5_var)

#cor mats
big5_cors <- all_corr_mats(big5_df)

#sheet names
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), times = 5)

big5_string <- rep(c("_ext","_agr", "_consc", "_es", "_intl"), each = 5)

names(big5_cors) <- str_c(cand_model_names , big5_string)
 
   
 cand_models <-  c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob")
  
 #cand_model_name = "fsr8vx"
wide_df <- function(cand_model_name){
     
     #combine dataframes for the same candidate model
     big5_cors[grep(paste0("^",{{cand_model_name}}),     names(big5_cors))] %>% 
     bind_rows() %>% 
       #generate a vector that can be used for pivot wider, so that names of the cols are pty
     mutate(pty_vec = rep(c("ext","agr", "consc", "es", "intl"), each = parse_number({{cand_model_name}}))) %>% 
       #to make it look like a cor mat
   pivot_wider(names_from = pty_vec, values_from = V1 )
   }
   
 big5_cors_mats <- map(cand_models, wide_df)
     
 names(big5_cors_mats) <- c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob")

neat_pub_big5 <- neat_pub_table(big5_cors_mats)
```

```{r results='asis'}
map(neat_pub_big5, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

```{r eval=FALSE}
#Write in excel sheet to send 
export_list("neat_pub_big5") 
```

### Multilanguage

**Multi-Language Seven factors**

-   Gregariousness - Talkative, Sociable, Comical, Expressive versus Shy, Bashful --

-   Self-Assurance - Bold, Masculine, Firm versus Fearful, Anxious, Timid Even

-   Temper - Patient versus Irritable, Harsh, Jealous, Emotional

-   Concern for Others - Warm, Courteous, Tolerant versus Cruel, Egotistical

-   Conscientiousness - Organized, Stern, Thrifty versus Disorganized, Unsystematic

-   Originality/Virtuosity - Philosophical, Clever, Complex versus Unreflective

-   Negative Valence - Corrupt, Evil, Good-for-nothing

```{r}
ml_var <-c(str_subset(names(data), pattern="scml"),              str_subset(names(data), pattern="sc_nval")) %>%
  #remove attraction var, it is an add on
         str_subset(pattern = "scml7att", negate = TRUE) 

ml_df <- select_Vars2(ml_var)
#cor_mat
ml_cors <- all_corr_mats(ml_df)
```

```{r}
#sheet names
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), times = 7)

ml_string <- rep(c("_gr","_sa", "_tmp", "_cfo", "_con", "_int", "_nval"), each = 5)

names(ml_cors) <- str_c(cand_model_names , ml_string)

#function
model_wise_cors <- function(string, cor_list){
  
  #create a string of all names
  select_names <- names(cor_list) %>% 
  str_subset(.,pattern = {{string}})
  
  #create a list with all models
  list = cor_list[names(cor_list) %in% select_names] 
  
  #convert the list to df
  plyr::ldply (list, data.frame) %>% 
    
    # #this will make ..1 = x1 for cleaner names
    # janitor::clean_names() %>% 
  mutate(var = word(.id, 2, sep = "_")) %>% 
    dplyr::select(var, V1, cand_model) %>%
    pivot_wider(names_from = var, values_from = V1)
}

ml_cors <- map(unique(cand_model_names), model_wise_cors, ml_cors)

names(ml_cors) <- unique(cand_model_names)

neat_pub_ml <- neat_pub_table(ml_cors)
```

```{r results='asis'}
map(neat_pub_ml, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

```{r eval=FALSE}
#Write in excel sheet to send 
export_list("neat_pub_ml") 
```

### Big 1

-   **Big One factors** Responsible, Patient, Warm, Clever, Sociable versus Cruel, Irritable, Disorganized, Corrupt, Dishonest

```{r}
big1_var <-str_subset(names(data), pattern="scb1")
big1_df <- select_Vars2(big1_var)

#cor_mat
big1_cors <- all_corr_mats(big1_df) %>% 
   map(., ~rename(., "scb1" = "V1"))
```

```{r}
#sheet names
cand_model_names <- c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob")

big1_string <- rep(c("_scb1.sd"), times =5)

names(big1_cors) <- str_c(cand_model_names , big1_string)

#publication ready table
#neat_pub_big1 <- neat_pub_table(big1_cors) 
```

```{r eval=FALSE, include=FALSE}
#Write in excel sheet to send - DON"T you need a combined Big 1 and 2 table
#export_list("neat_pub_big1") 
```

### Big 2

-   **Big Two factors** - Morality and Social Propriety - Courteous, Patient, Tolerant, Responsible versus Cruel, Harsh, Irritable, Reckless, Corrupt, Egotistical

-   Dynamism/Dominance/Deference - Expressive, Talkative, Bold, Clever, Sociable, Humorous, Good-looking versus Timid, Dull, Bashful

```{r}
big2_var <-str_subset(names(data), pattern="scb2") %>% 
             str_subset(pattern="10")

big2_df <- select_Vars2(big2_var)

#cor_mat
big2_cors <- all_corr_mats(big2_df)
```

```{r}
#sheet names
cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), times = 2)
big2_string <- rep(c("_scb2.s10","_scb2.d10"), each = 5)
names(big2_cors) <- str_c(cand_model_names , big2_string)

big2_cors <- map(unique(cand_model_names), model_wise_cors, big2_cors)
names(big2_cors) <- unique(cand_model_names)

#publication ready table
#neat_pub_big2 <- neat_pub_table(big2_cors)
```

```{r eval=FALSE, include=FALSE}
#Write in excel sheet to send - DON"T you need a combined Big 1 and 2 table
#export_list("neat_pub_big2") 
```

```{r}
# Combined Big1 and Big2 table
neat_pub_big1n2 <- map2(big1_cors,big2_cors, left_join) %>% 
                       neat_pub_table()
```

```{r results='asis'}
map(neat_pub_big1n2, ~DT::datatable(.x,  options = list(columnDefs = list(list(className = 'dt-center', targets = 0:4)))) %>%
      htmltools::tagList() %>%
      print())
```

```{r eval=FALSE}
#Write in excel sheet to send 
export_list("neat_pub_big1n2") 
```
