---
title: "PCA"
author: "Vinita Vader"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(psych)
library(corrr)
library(readxl)
```

# Varimax 5 candidate model 
```{r}
data <- rio::import(here::here("data", "data.csv"), setclass = "tbl_df") %>% 
  rio::characterize() %>% 
  janitor::clean_names() %>% 
  dplyr::select(angel:young)

pca_vrx5 <- principal(data, nfactors = 5, rotate = "varimax")
pca_vrx5 <- fa.sort(pca_vrx5)

  
vrx5_loadings <-  unclass(loadings(pca_vrx5))%>% 
    as_tibble(rownames = "id")
 

rio::export( vrx5_loadings, "pca_vrx5.xlsx")

```

```{r}
fs_data <- rio::import(here::here("data", "typenoun_FSonly1_5_8_13_32.xlsx"), setclass = "tbl_df") %>% 
  rio::characterize() %>% 
  janitor::clean_names() %>% 
  dplyr::select(fsr1unr1, fsr5vx1:fsr5vx5, fsr8vx1:fsr8vx8, fsr13ob1:fsr13ob13, fsz32ob1:fsz32ob32)

cor_mat <- fs_data %>% 
  cor() %>% 
  round(3) %>% 
as_tibble(rownames = "id")

rio::export( cor_mat, "cor_mat_1_5_8_13_32.xlsx")
```


# Addendum 1

We will generate correlations matrices showing the relation to the 1, 5, 8, and 13-factor models' variables to the following 'external/etic variables': the Dutch and the German type-noun factors, the Big Five, Big Three, Big Two, and Big One structures as well the Multi-Language Seven set.

#### Import data
```{r}
#data with all fs and type-nouns 
data <- rio::import(here::here("data", "typenoun.sav"), setclass = "tbl_df") %>% 
  rio::characterize() %>% 
  janitor::clean_names()

#data.frame(names(data)) %>% View

#data for the factor scores of 1,5,8,13 and 32 factor candidate models 
fs_candModels <- rio::import(here::here("data", "typenoun_FSonly1_5_8_13_32.xlsx"), setclass = "tbl_df") %>% 
  rio::characterize() %>% 
  janitor::clean_names()


```

#### Functions
```{r}
#function for fs_candModels data
select_Vars <- function(varNames){
  fs_candModels %>% 
    dplyr::select_at(vars(all_of((varNames))))
}

#function for data
select_Vars2 <- function(varNames){
  data %>% 
    dplyr::select_at(vars(all_of((varNames))))
}

```



```{r}
var_names_string <- function(actual_string){
   extract_no <- str_extract_all({{actual_string}},"\\(?[0-9,.]+\\)?") %>% 
    unlist() %>% 
    as.numeric()
   
   var_names <- paste0({{actual_string}}, 1:extract_no)
    var_names
}

cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), each = 2)

fs_var_names <- map(cand_model_names, var_names_string)

#names(var_names_list) <- rep(c("var_1", "var_5", "var_8", "var_13", "var_32"), each = 2)

list_fs <- fs_var_names %>% 
 purrr::map(select_Vars)
```


##### **German male-target factors**  
M1 - Weakling, Sissy, Chicken, Coward, Softy  
M2 - Smart-aleck, Wise-guy, Pain-in-the-neck, Liar, Loudmouth  
M3 - Thinker, Intellectual, Genius, Egghead, Quick-thinker  
M4 - Joker, Clown, Comedian, Life-of-the-party, Jester  |
M5 - Ladies'-man, Lady-killer, Playboy, Stud, Womanizer 
M6 - Recluse, Loner, Skeptic,  Nag, Individual  
M7 - Stickler, Careerist, Born-fighter, High-flier  

```{r}
g_m_var <- c(paste0("sc_gm", 1:7))
german_man_df <- select_Vars2(g_m_var)
```


#####  **German female-target factors ** 
F1 - Loudmouth, Nag, Nuisance, Pest, Pain-in-the-neck 
F2 - Thinker, Authority, Intellectual, Egghead, Quick-thinker 
F3 - Joker, Comedian, Life-of-the-party, Pal 
F4 - Conservative, Bore, Sleephead, Coward, Hanger-on 
F5 - Pessimist, Chicken, Dreamer, Daydreamer, Skeptic 
F6 - Beauty, Careerist, Materialist, Sex-object, Fashion-plate
```{r}
g_w_var <- c(paste0("sc_gw", 1:6))
german_woman_df <- select_Vars2(g_w_var)
```

#####  **German table**
```{r}
german_list<- list(german_man_df, german_woman_df)

german_cors <- mapply(x= list_fs, y = german_list, FUN=cor) 


cand_model_names <- rep(c("fsr1unr", "fsr5vx", "fsr8vx", "fsr13ob", "fsz32ob"), each = 2)

mw_string <- rep(c("_m","_w"), times = 5)


names(german_cors) <- str_c(cand_model_names , mw_string)



```


#####  **Dutch self factors** 
Malignity - Cheater, Monster, Arch-villain, False-friend 
Anxiety - Chicken, Scaredy-cat, Coward, Bore 
Extraversion - Boaster, Merrymaker, Chatterer, Chatterbox 
Culture - Strategist, Philosopher, Thinker, Intellectual 
Antagonism - Troublemaker, Nuisance, Obstructionist, Oppositionalist 
Perseverance - Go-getter, Worker, Workhorse 
Materialism - Capitalist, Leader, Authority, Boss
```{r}
d_s_var <- c(paste0("sc_ds", 1:7))
dutch_self_df <- select_Vars2(d_s_var)
```

##### **Dutch-partner factors** 
Malignity - Monster, Moron, Vandal, Pain-in-the-neck 
Extraversion - Clown, Comedian, Merrymaker 
Anxiety - Scaredy-cat, Worrywart, Coward, Chicken Antagonism - Know-it-all, Oppositionalist, Obstructionist 
Culture - Philosopher, Poet, Intellectual, Anarchist 
Perseverance - Go-getter, Fighter, Worker, Workhorse 
Colourlessness - Stoic, Pragmatist, Chameleon, Softy

```{r}
d_p_var <- c(paste0("sc_dp", 1:7))
dutch_peer_df <- select_Vars2(d_p_var)
```

```{r}
dutch_list<- list(dutch_self_df, dutch_peer_df)

dutch_cors <- mapply(x= list_fs, y = dutch_list, FUN=cor) 
```



```{r echo=FALSE, eval=FALSE}
#Write in excel sheet to send 
filename <- "/Users/vinitavader/Desktop/Type-noun/data/dutch_cors.xlsx"

rio::export(list(dutch_cors), check.rows = FALSE, filename)
```


#####  **Big Five factors** 
Extraversion - Bold, Talkative, Sociable versus Bashful, Shy, Timid Agreeableness - Warm, Tolerant, Lenient versus Harsh, Stern, Cruel, Sly 
Conscientiousness - Organized, Logical, Firm versus Disorganized, Unsystematic, Scatterbrained 
Emotional Stability - Anxious, Fearful, Emotional, Jealous Intellect - Philosophical, Complex, Clever, Unconventional versus Conventional, Traditional, Unreflective

```{r}
big5_var<- c("scb5_i","scb5_ii","scb5_iii","scb5_iv","scb5_v")
big5_df <- select_Vars(data, big5_var)
```


##### **Multi-Language Seven factors** 
Gregariousness - Talkative, Sociable, Comical, Expressive versus Shy, Bashful 
Self-Assurance - Bold, Masculine, Firm versus Fearful, Anxious, Timid 
Even Temper - Patient versus Irritable, Harsh, Jealous, Emotional Concern for Others - Warm, Courteous, Tolerant versus Cruel, Egotistical 
Conscientiousness - Organized, Stern, Thrifty versus Disorganized, Unsystematic 
Originality/Virtuosity - Philosophical, Clever, Complex versus Unreflective  
Negative Valence - Corrupt, Evil, Good-for-nothing
```{r}

```


##### **Big One factors**
Responsible, Patient, Warm, Clever, Sociable versus Cruel, Irritable, Disorganized, Corrupt, Dishonest
```{r}
#data %>% names %>% data.frame() %>% View
```

#####  **Big Two factors**  Morality and Social Propriety - Courteous, Patient, Tolerant, Responsible versus Cruel, Harsh, Irritable, Reckless, Corrupt, Egotistical  Dynamism/Dominance/Deference - Expressive, Talkative, Bold, Clever, Sociable, Humorous, Good-looking versus Timid, Dull, Bashful
```{r}

```
